Analysis Stand Features 

### 2017-05-16 analysis/analysis_stand_features.Rmd
update md
change format table

@@

# Prepare Data
```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

  summ_comparison <- summ_values %>% left_join(df_letter, by='site')

@@

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

@@

# Prepare Data
```{r, echo=FALSE}
# machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

  summ_comparison <- summ_values %>% left_join(df_letter, by='site') %>% as.data.frame()

@@

```{r}
# Get name of variables 
variables <- compe %>% dplyr::select(ba:dnn) %>% names() %>% rbind()
# Add topo and focal tree variables 
nombres <- c(variables, 'mde','slope', 'dn', 'h')

out <- c()

for (i in nombres){ 
  # name of aov object
  aov_name <- paste0('aov_',i)
  # get aov_object 
  aux <- get(aov_name)
  # get summ comparison dataframe 
  aux2 <- aux$summ_comparison
  out <- rbind(out, aux2)
}

out2 <- out %>% dplyr::select(site, mean, sd, tukey, mivar = variable)

out2

# See this solution 
# http://stackoverflow.com/questions/39066811/long-to-wide-with-dplyr
out3 <- gather(out2, variable, value, mean, sd, tukey) %>% 
  unite(var, variable, site) %>% 
  spread(var, value)

out3 <- out3 %>% dplyr::select(mivar, mean_CA_High, sd_CA_High, tukey_CA_High,
                 mean_CA_Low, sd_CA_Low, tukey_CA_Low,
                 mean_SJ_High, sd_SJ_High, tukey_SJ_High,
                 mean_SJ_Low, sd_SJ_Low, tukey_SJ_Low)
